Embracing the Laws of Physics: \\ Three Reversible Models of Computation

### 2018-06-15 survey/survey.tex
cleaning up conclusion structure

Possible extensions; quest for other principles; other data models; graphs; HoTT

@@

Natural numbers: fold/unfold

@@

@@

@@

%%%
\subsection{Conservation of Information, Information Effects, and Duality}

Talk about conservation of information in biology, computer science,
evolutionary computing, and search. (See
\url{http://www.evolutionnews.org/2012/08/conservation_of063671.html}.

@@

Mention connections to negative, fractional, and algebraic numbers

@@

\bibliographystyle{unsrt}
%\pagestyle{headings}
\bibliography{cites}
\end{document}

@@

\begin{comment}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Theseus: Types and Simple Isomorphisms}
\label{theseusI}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Parametrized Maps}
\label{theseusII}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Iteration Labels}
\label{theseusIII}
\label{add1}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusion}
\label{conc}

>>>>

We include with a collection of open problems and avenues for further research.

@@

Inductive types: Natural numbers: fold/unfold

@@

Other infinite type: Mention connections to negative, fractional, and
algebraic numbers

@@

other data models; graphs; HoTT

@@

%%%
\subsection{Information Effects}

@@

@@

\bibliographystyle{unsrt}
\bibliography{cites}
\end{document}

@@

\begin{comment}
\section{Theseus: Types and Simple Isomorphisms}
\label{theseusI}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Parametrized Maps}
\label{theseusII}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Iteration Labels}
\label{theseusIII}
\label{add1}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusion}
\label{conc}
